Liveness-Based Garbage Collection for Lazy Languages

### 2016-02-03 paper/paper.tex
spell check

In  this work  we show  that  static analysis  of heap  data can  help
garbage  collectors   in  reclaiming   more  garbage.    The  specific
contributions of this paper are
\added{
\begin{itemize}
\item We propose a liveness based GC scheme for a lazy
  first order functional  language and prove its  correctness.  To the
  best  of our  knowledge, this  is the  first work  on liveness-based
  GC   for    lazy    languages.    All    previous
  attempts~\cite{shaham01heap,  ran.shaham-sas03,  shaham02estimating,
    asati14lgc,    karkare06effectiveness}   have    involved   either
  imperative  or  eager  functional  languages.   The  novely  of  our
  approach is in  handling of  liveness of  functional values  (i.e.,
  closures), an issue that arises due to laziness.

@@

Simplifiers~\cite{ONeill} are abstractly described as lightweight
daemons that attach themselves to program data and, when activated, improve
the efficiency of the program. Our liveness-based GC
is an instance of a  simplifier which is tightly coupled with garbage collectors.  The
approach that is closest to the  method described in this paper is the
liveness-based garbage collector implemented
in~\cite{karkare07liveness,asati14lgc} and address eager languages. We
extend this to handle lazy evaluation and closures.

%% A similar approach has been suggested in~\cite{ONeill} where they suggest augmenting GC with extra information using {\it simplifiers}.

>>>>

In  this work  we show  that  static analysis  of heap  data can  help
garbage  collectors   in  reclaiming   more  garbage.    The  specific
contributions of this paper are
\added{
\begin{itemize}
\item We propose a liveness based GC scheme for a lazy
  first order functional  language and prove its  correctness.  To the
  best  of our  knowledge, this  is the  first work  on liveness-based
  GC   for    lazy    languages.    All    previous
  attempts~\cite{shaham01heap,  ran.shaham-sas03,  shaham02estimating,
    asati14lgc,    karkare06effectiveness}   have    involved   either
  imperative  or  eager  functional  languages.   The  novelty  of  our
  approach is in  handling of  liveness of  functional values  (i.e.,
  closures), an issue that arises due to laziness.

@@

Simplifiers~\cite{ONeill}  are  abstractly  described  as  lightweight
daemons that  attach themselves to  program data and,  when activated,
improve the  efficiency of the  program. Our liveness-based GC  can be
seen as  an instance  of a  simplifier which  is tightly  coupled with
garbage  collectors.   The approach  that  is  closest to  the  method
described  in  this  paper  is the  liveness-based  garbage  collector
implemented  in~\cite{karkare07liveness,asati14lgc} and  address eager
languages. We extend this to handle lazy evaluation and closures.

%% A similar  approach has been suggested  in~\cite{ONeill} where they
%% suggest   augmenting  GC   with   extra   information  using   {\it
%% simplifiers}.
